opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-12-08 chapters/04_our_dataset.tex
Added percentages to database overview

\begin{table}[!htb]
\centering
\caption{opXRD database entries}
\label{tab:merged}
\scalebox{0.92}{
\begin{tabular}{@{}clcccccl@{}}
\toprule
Institution & No. Patterns & Comp. & Spg & Lattice & Unit Cell & Research Project \\ 
\midrule
CNRS        & \qquad 1052          & \cmark   & \cmark   & \cmark   & \cmark   & Extracted from the COD                 \\ 
HKUST(GZ)   & \qquad 21           & \cmark   & \cmark   & \cmark   & \cmark   & Phase identification reference database \\ 
USC         & \qquad 338          & \cmark   & \cmark   & \cmark   & \xmark   & Study of CuNi and CuAl alloys          \\ 
EMPA        & \qquad 790          & \cmark   & \cmark   & \xmark   & \xmark   & Tin halide perovskites, Zn-V-N library \\ 
INT         & \qquad 19,780        & \xmark   & \xmark   & \xmark   & \xmark   & Compilation of various projects        \\ 
IKFT        & \qquad 64           & \xmark   & \xmark   & \xmark   & \xmark   & Commercial catalysts, bulk materials   \\ 
LBNL        & \qquad n/a          & \xmark   & \xmark   & \xmark   & \xmark   & Time series recordings of Perovskites  \\ 
\bottomrule
\end{tabular}}
\end{table}

@@

>>>>

\newcommand{\partialcheck}[1]{\textcolor{orange}{\ding{52}(#1\%)}}

\begin{table}[!htb]
\centering
\caption{opXRD database entries}
\label{tab:merged}
\scalebox{0.90}{
\begin{tabular}{@{}lllllll@{}}
\toprule
Institution & No. Patterns & Comp. & Spg & Lattice & Atom coords. & Research Project \\ 
\midrule
CNRS        & \qquad 1052          & \cmark   & \partialcheck{85}   & \cmark   &  \partialcheck{85}   & Extracted from the COD \\ 
HKUST(GZ)   & \qquad 21           & \cmark   & \cmark   & \cmark   & \cmark   & Phase identification reference database \\ 
USC         & \qquad 338          & \cmark   & \cmark   & \partialcheck{90}   & \xmark   & Study of CuNi and CuAl alloys          \\ 
EMPA        & \qquad 790          & \cmark   & \partialcheck{63}   & \xmark   & \xmark   & Tin halide perovskites, Zn-V-N library \\ 
INT         & \qquad 19,780        & \xmark   & \xmark   & \xmark   & \xmark   & Compilation of various projects        \\ 
IKFT        & \qquad 64           & \xmark   & \xmark   & \xmark   & \xmark   & Commercial catalysts, bulk materials   \\ 
LBNL        & \qquad n/a          & \xmark   & \xmark   & \xmark   & \xmark   & Time series recordings of Perovskites  \\ 
\bottomrule
\end{tabular}}
\end{table}

@@

% Paragraph by Gregoire Heymans

\subsubsection*{\textit{In situ} XRD (RT $\le$ T$_{annealing}$ $\le$ 850$\degree$C)}

The phase evolution of the Mn-Sb-O system varying with annealing temperature was measured using the \textit{in situ} XRD (Rigaku-SmartLab3kW XRD, Figure \ref{fig:stability} (a)). This tool operates with SmartLab Studio II software, which is able to measure the X-ray diffraction during the annealing process. This enables to show directly all the phase transitions when annealing in various atmospheres such as O$_2$, Ar and NH$_3$. This device can theoretically operate up to 1000$\degree$C in a 20\% O$_2$ atmosphere. For safety reasons, phase transitions are analyzed with the \textit{in situ} XRD tool up to 850$\degree$C in this work.

Most of the \textit{in situ} experiments were performed under an air-like 20\% O$_2$ and 80\% argon (Ar) environment is chosen (Ar flow: 50 sccm, O$_2$ flow: 10 sccm). When a 100\% Ar environment is fixed, an Ar flow of 60 sccm is input.

Concerning the geometry, the Bragg-Brentano (BB) mode is preferred because it is more adapted in the analysis of scarce phases (i.e., MnSb$_2$O$_6$ rutile). The step is 0.01$\degree$ and the scanning rate is 10$\degree$/min. The step gives information about the resolution and the scanning rate (or speed duration time) results in the quality of the signal-to-noise ratio.

Figure \ref{fig:temp} shows the temperature profile during the \textit{in situ} XRD measurements. The temperatures used to annalyze the crystal structure of the Mn-Sb-O system were chosen depending on the number of phase transitions appearing for a certain temperature range. As explained in details in chapter \ref{res}, few changes in the crystal structure appear between RT and 300$\degree$C and phase transitions appeared from 300$\degree$C until 850$\degree$C. No phase transition appeared when cooling down. Therefore, the crystal structure was measured every 100$\degree$C between RT and 300$\degree$C; every 50$\degree$C between 300$\degree$C and 850$\degree$C; and every 200$\degree$C when cooling down. The heating and cooling rates are fixed for all the experiments at 50$\degree$C/min and the holding time is fixed at 2 min.

% end of Gregoire Heymans
